Neural Textures make Better Simulators ``I can't believe it's not real!"

### 2022-06-12 CORL/example.tex
Created graveyard section and moved dataset_explanation figure into it
Added data subsection of results

TODO: Describe what UVL is ; 
Formulate the setting: What our inputs are and the targets are and what we learn (a neural texture function) and how we can take advantage of it for robotic learning.
Don't go into details; just say 'its a black box function'

TODO: Add UV to the fourier feature diagram.

TODO: Create subfigures with subcaptions. 
2a: Nothing but UVL=UV+L
2b. 3d uvl axis to texture pack (drew on whiteboard)
2c. Skip over the translation network and show a pretty robot arm picture

This is the formulatoin section; not data section. Dont talk about how many photos we use etc.

JUST IN CASE THINGS ARE ERASED:
We learn neural texture corresponding to each object, where each texture is represented as a function mapping... 
The idea is to learn object textures as a set of continuous functions from a set of (unlabeled) real images, and use them to generate realistic images.
Given a 3D structure of the scene represented with a UVL image, the learned neural textures will translate them into a realistic image.
When used for the robot learning, this enables learnable, realistic sim2real of robot training images.

IN THE INTRODUCTION: How we're using a neural neural network network texture. Also in related works.

TODO: Replace neural texture in figure 3 with axis, and treat it as a function that takes UV in with an arrow pointing to it.

BREAK IT DOWN APPROACH:
Don't have any pictures. Have breakdown where we add new things in multiple figures.
First figure: Just image translation. 
Seconf:
Third:
Etc...

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=270pt]{../images/uvl_explanation.pdf}
	\end{center}
	\caption{
		This diagram shows the purpose of a UVL image.
		A UVL scene is an image that has three channels: RGB.
		R and G are used for U and V, and B is used for L.
		L stands for Label, and determines which part of the synthetic image will get which texture.
		The U and V coordinates correspond to positions on each texture,
		telling it how to project the textures onto the 3d objects represented in the UVL scene.
		The darkest shade of blue corresponds to the 1st texture, and the next darkest shade of blue corresponds to the 2nd texture etc.
		}
	\label{fig:uvl_explanation}
\end{figure}

In this paper, we'll mostly focus on a hand-collected dataset that involves three alphabet blocks that are moved across a table.
Alphabet blocks were chosen because they all have the same geometry (a cube), but have very distinct semantic textures that will make temporal inconsistency obvious to the human eye.
This dataset is analogous to data that would be collected for a third-person robotic grasping task.
However, other objects (such as cans of soda, apples, cloves of garlic, etc) are also for generating other results in this paper. ((TODO: Detail the five object tests and five cube tests and other stuff like shiny cans etc)).

There are two components to this dataset: Simulated data in the form of UVL scenes, and photographs.
The camera in the simulation is positioned in approximately the same place as the real camera, with approximately the same field of view.
In both domains of this dataset, the camera never moves. Instead, the objects are randomly positioned and rotated on the table.
In both the simulation and in real life, these objects are randomly translated along the x and y-axis of the table, as well as rotated on the z-axis.

There are 200 photographs in this dataset, and they are recorded as RGB jpg images.
There are 3000 synthetic images in this dataset, in the form of UVL images.
These UVL images are also encoded as RGB images, but provide information about the geometry of a scene.
UVL images are composed of both a UV map and a label map and are summarized in figure \ref{fig:uvl_explanation}.
To avoid positional rounding errors, UVL images are encoded as EXR files: an image format that supports floating-point values.

The pixels in a UVL image are visualizable in RGB space because, like RGB images, each pixel is a vector with 3 values. The first two channels, U and V, are floating point values between 0 and 1. The L channel is also a floating point value between 0 and 1, it has a second meaning. There are only a finite number of label values (corresponding to the number of learnable textures). The rank of a particular L value is used to index these textures.

In the three-cube dataset we have 4 textures, and UVL scenes contain label values $l \in [\frac{0}{3}, \frac{1}{3},\frac{2}{3}, \frac{3}{3}]$. A pixel in a UVL scene $l=\frac{2}{3}$ will get indexed to the third texture, because $\frac{2}{3}$ is the third smallest label value.

Domain A and B
p hat
s hat

@@

	\begin{figure}[H]
		\begin{center}
			\includegraphics[width=400pt]{../images/learnable_textures.pdf}
		\end{center}
		\caption{
			This figure illustrates how the neural textures are calculated in figure \ref{fig:main_diagram}. They are fully differentiable, and represented continuously along the texture's U and V axes using fourier feature networks.
		}
		% For each texture, there is a separate Fourier feature network (Fourier features fed into a pixel-wise MLP) that will take in Fourier features as inputs, and output an RGB image using the method described in \citet{fourier_feature_networks}.
		% We found this method gave better results than storing each differentiable texture as a raster matrix of pixels, as well as being faster to train.
		% During inference, you can store the results of this MLP as a raster image of arbitrarily large resolution, saving both time and VRAM.
		\label{fig:learnable_textures}
	\end{figure}

@@

\section{Results}
\label{sec:results}

@@

>>>>

% TODO: Describe what UVL is ; 
% Formulate the setting: What our inputs are and the targets are and what we learn (a neural texture function) and how we can take advantage of it for robotic learning.
% Don't go into details; just say 'its a black box function'

% TODO: Add UV to the fourier feature diagram.

% TODO: Create subfigures with subcaptions. 
% 2a: Nothing but UVL=UV+L
% 2b. 3d uvl axis to texture pack (drew on whiteboard)
% 2c. Skip over the translation network and show a pretty robot arm picture

% This is the formulatoin section; not data section. Dont talk about how many photos we use etc.

% JUST IN CASE THINGS ARE ERASED:
% We learn neural texture corresponding to each object, where each texture is represented as a function mapping... 
% The idea is to learn object textures as a set of continuous functions from a set of (unlabeled) real images, and use them to generate realistic images.
% Given a 3D structure of the scene represented with a UVL image, the learned neural textures will translate them into a realistic image.
% When used for the robot learning, this enables learnable, realistic sim2real of robot training images.

% IN THE INTRODUCTION: How we're using a neural neural network network texture. Also in related works.

% TODO: Replace neural texture in figure 3 with axis, and treat it as a function that takes UV in with an arrow pointing to it.

% BREAK IT DOWN APPROACH:
% Don't have any pictures. Have breakdown where we add new things in multiple figures.
% First figure: Just image translation. 
% Seconf:
% Third:
% Etc...

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=270pt]{../images/uvl_explanation_minimal.pdf}
	\end{center}
	\caption{
		% This diagram shows the purpose of a UVL image.
		A UVL scene is an image that has three channels: RGB.
		R and G are used for U and V, and B is used for L.
		L stands for Label, and determines which part of the synthetic image will get which texture.
		The U and V coordinates correspond to positions on each texture,
		telling it how to project the textures onto the 3d objects represented in the UVL scene.
		The darkest shade of blue corresponds to the 1st texture, and the next darkest shade of blue corresponds to the 2nd texture etc.
		}
	\label{fig:uvl_explanation}
\end{figure}

% In this paper, we'll mostly focus on a hand-collected dataset that involves three alphabet blocks that are moved across a table.
% Alphabet blocks were chosen because they all have the same geometry (a cube), but have very distinct semantic textures that will make temporal inconsistency obvious to the human eye.
% This dataset is analogous to data that would be collected for a third-person robotic grasping task.
% However, other objects (such as cans of soda, apples, cloves of garlic, etc) are also for generating other results in this paper. ((TODO: Detail the five object tests and five cube tests and other stuff like shiny cans etc)).

% There are two components to this dataset: Simulated data in the form of UVL scenes, and photographs.
% The camera in the simulation is positioned in approximately the same place as the real camera, with approximately the same field of view.
% In both domains of this dataset, the camera never moves. Instead, the objects are randomly positioned and rotated on the table.
% In both the simulation and in real life, these objects are randomly translated along the x and y-axis of the table, as well as rotated on the z-axis.

% There are 200 photographs in this dataset, and they are recorded as RGB jpg images.
% There are 3000 synthetic images in this dataset, in the form of UVL images.
% These UVL images are also encoded as RGB images, but provide information about the geometry of a scene.
% UVL images are composed of both a UV map and a label map and are summarized in figure \ref{fig:uvl_explanation}.
% To avoid positional rounding errors, UVL images are encoded as EXR files: an image format that supports floating-point values.

% The pixels in a UVL image are visualizable in RGB space because, like RGB images, each pixel is a vector with 3 values. The first two channels, U and V, are floating point values between 0 and 1. The L channel is also a floating point value between 0 and 1, it has a second meaning. There are only a finite number of label values (corresponding to the number of learnable textures). The rank of a particular L value is used to index these textures.

% In the three-cube dataset we have 4 textures, and UVL scenes contain label values $l \in [\frac{0}{3}, \frac{1}{3},\frac{2}{3}, \frac{3}{3}]$. A pixel in a UVL scene $l=\frac{2}{3}$ will get indexed to the third texture, because $\frac{2}{3}$ is the third smallest label value.

% %===============================================================================

% Domain A and B
% p hat
% s hat

@@

	\begin{figure}[H]
		\begin{center}
			\includegraphics[width=400pt]{../images/learnable_textures.pdf}
		\end{center}
		\caption{
			This figure illustrates how the neural textures are calculated in figure \ref{fig:main_diagram}. They are fully differentiable, and represented continuously along the texture's U and V axes using fourier feature networks.
		}
		% For each texture, there is a separate Fourier feature network (Fourier features fed into a pixel-wise MLP) that will take in Fourier features as inputs, and output an RGB image using the method described in \citet{fourier_feature_networks}.
		% We found this method gave better results than storing each differentiable texture as a raster matrix of pixels, as well as being faster to train.
		% During inference, you can store the results of this MLP as a raster image of arbitrarily large resolution, saving both time and VRAM.
		\label{fig:learnable_textures}
	\end{figure}
	s

@@

\section{Results}

\subsection*{Data}

Here I detail the datasets used in the results section. 
Every dataset has two sets of images: UVL scenes and photographs. They are all unpaired, and have RGB values ranging from 0 to 1.

The first dataset to mention is the three-block dataset.  
It has 300 photos and 2000 UVL scenes. It features a table with three alphabet blocks on a table, which are randomly translated along the X and Y axes and rotated randomly along the Z axis. Each photograph features these three cubes with a random position and rotation.

[[Insert photographs and UVL maps here; a digram showing each dataset we describe here and 1 or two samples of each domain in each dataset]]

% In this paper, we'll mostly focus on a hand-collected dataset that involves three alphabet blocks that are moved across a table.
% Alphabet blocks were chosen because they all have the same geometry (a cube), but have very distinct semantic textures that will make temporal inconsistency obvious to the human eye.
% This dataset is analogous to data that would be collected for a third-person robotic grasping task.
% However, other objects (such as cans of soda, apples, cloves of garlic, etc) are also for generating other results in this paper. ((TODO: Detail the five object tests and five cube tests and other stuff like shiny cans etc)).

% There are two components to this dataset: Simulated data in the form of UVL scenes, and photographs.
% The camera in the simulation is positioned in approximately the same place as the real camera, with approximately the same field of view.
% In both domains of this dataset, the camera never moves. Instead, the objects are randomly positioned and rotated on the table.
% In both the simulation and in real life, these objects are randomly translated along the x and y-axis of the table, as well as rotated on the z-axis.

% There are 200 photographs in this dataset, and they are recorded as RGB jpg images.
% There are 3000 synthetic images in this dataset, in the form of UVL images.
% These UVL images are also encoded as RGB images, but provide information about the geometry of a scene.
% UVL images are composed of both a UV map and a label map and are summarized in figure \ref{fig:uvl_explanation}.
% To avoid positional rounding errors, UVL images are encoded as EXR files: an image format that supports floating-point values.

% The pixels in a UVL image are visualizable in RGB space because, like RGB images, each pixel is a vector with 3 values. The first two channels, U and V, are floating point values between 0 and 1. The L channel is also a floating point value between 0 and 1, it has a second meaning. There are only a finite number of label values (corresponding to the number of learnable textures). The rank of a particular L value is used to index these textures.

% In the three-cube dataset we have 4 textures, and UVL scenes contain label values $l \in [\frac{0}{3}, \frac{1}{3},\frac{2}{3}, \frac{3}{3}]$. A pixel in a UVL scene $l=\frac{2}{3}$ will get indexed to the third texture, because $\frac{2}{3}$ is the third smallest label value.

% %===============================================================================

% Domain A and B
% p hat
% s hat

\label{sec:results}

@@

\section*{Graveyard}

Here I put things I won't include in the paper or appendix, but want to keep for reference until submission
